cardinalR: Generating interesting high-dimensional data structures

### 2025-10-14 paper-cardinalR.Rmd
Added implementation figure

The `cardinalR` package is built on a modular framework where individual geometric generators (e.g., Gaussian, cone, sphere) create well-defined shapes. The main function, `gen_multicluster()`, combines these shapes into a single dataset by applying scaling, rotation, and translation through `gen_rotation()`. Each generated shape is assigned a unique cluster label. This design allows flexible construction of complex, high-dimensional structures for evaluating clustering and dimension reduction methods. Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:workflow)', '\\@ref(fig:workflow)'))` illustrates the workflow of `gen_multicluster()`.

```{r workflow, out.width = "100%", fig.pos="H", fig.cap="Workflow of.", eval=FALSE}
knitr::include_graphics("figures/cardinalR.pdf")
```

>>>>

The `cardinalR` package is built on a modular framework where individual geometric generators (e.g., Gaussian, cone, sphere) create well-defined shapes. The main function, `gen_multicluster()`, combines these shapes into a single dataset by applying scaling, rotation, and translation through `gen_rotation()`. Each generated shape is assigned a unique cluster label. This design allows flexible construction of complex, high-dimensional structures for evaluating clustering and dimension reduction methods. Figure `r '\\@ref(fig:workflow)'` illustrates the workflow of `gen_multicluster()`.

```{r workflow, out.width = "100%", fig.pos="H", fig.cap="Workflow for generating high-dimensional clustered data. The user specifies input parameters (number of points, clusters, cluster shapes, scaling, rotation, and optional background noise). Clusters are generated iteratively, transformed, optionally augmented with Gaussian noise dimensions, combined, and labeled, resulting in the final dataset."}

knitr::include_graphics("figures/cardinalR_workflow.png")
```

### 2025-10-14 paper-cardinalR.tex
Added implementation figure

>>>>

\begin{figure}[H]
\includegraphics[width=1\linewidth]{figures/cardinalR_workflow} \caption{Workflow for generating high-dimensional clustered data. The user specifies input parameters (number of points, clusters, cluster shapes, scaling, rotation, and optional background noise). Clusters are generated iteratively, transformed, optionally augmented with Gaussian noise dimensions, combined, and labeled, resulting in the final dataset.}\label{fig:workflow}
\end{figure}
